Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-05-13 paper/main.tex
add info (stimuli, procedurem, fmri acq./setup) from Sengupta (2016)

We used data from three publicly available datsets as part of the studyforrest
dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already
been used by other research groups for independent research questions before.

We used fMRI data from 14 subjects who took part in three different studies. Namely, the same subjects were

a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding}.
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}, a dataset already used by
\citep{ben2018hippocampal}. c) participating in a dedicated block-wise visual
localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by
\citep{jiahui2019predicting}.

@@

\todo[inline]{Alles um Sengupta ergänzen}

@@

\todo[inline]{inner join von AO \& AV: N=14; AO: N=19; es fehlt in beiden VP10;
Angaben zu Alter (Durchschnitt; ggf. Range) und Geschlecht sind folglich falsch}

In the AO study, 19 participants (all right-handed, age 21–38 years, mean age
26.6 years, 12 male) listened to the German audio-description
\citep{ForrestGumpGermanAD} of the movie ``Forrest Gump''
\citep{ForrestGumpMovie} as an additional audio track for visually impaired
listeners on Swiss public television. In the AV study, the same 14 participants
(21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}. All participants reported to have normal hearing, normal or corrected-to-normal vision, and no known history of neurological disorders.

\todo[inline]{Sengupta (2016)}
In the LOC study\dots

In both studies, participants received monetary compensation and gave written informed consent for their participation and for public sharing of all obtained data in anonymized form. The studies had prior approval by the Ethics Committee of Otto-von-Guericke University of Magdeburg, Germany.

\subsection{Stimuli}
% stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of
the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
temporally aligned audio-description (i.e. the audio-only variant of the movie)
that was broadcast as an additional audio track for visually impaired listeners
on Swiss public televinsion \citep{ForrestGumpGermanAD}.

% difference in audio track AV vs. AO
The plot of the movie is already carried by an off-screen voice of the main
character Forrest Gump.  In the largely identical audio-description, a male
narrator additionally describes essential aspects of the visual scenery when
there is no off-screen voice, dialog, or other relevant auditory content.

% stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$2h
\citep{hanke2014audiomovie, hanke2016simultaneous}. Both stimuli were further
processed (filtering, volume adjustments) to improve audibility during MRI
scanning. Finally, each stimulus was split into eight segments of approximately
15 minutes.  Except for the first movie segment, each segment started with a
snippet of at least six seconds immediately preceding the movie scene boundary
used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}.

\todo[inline]{Sengupta (2016)}

@@

\subsection{Procedure}

In both [all three] studies, participants filled out a questionnaire on their
basic demographic information and familiarity with the audio-description or the
movie. Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively. Audio-description and movie segments were presented in
chronological order with four segments in two fMRI sessions respectively.
Between sessions, participants left the scanner for a break with a flexible
duration. Structural images were obtained during the first study on a day
different from the fMRI session.

@@

\todo[inline]{irrelevantes kürzen}
In both studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.

In the AO study, visual instructions were presented on a rear-projection screen
inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue. [The screen contained a solid black ``fixation'' dot that faded in and
out at the beginning and end of a movie segment.]

In the AV study, visual instructions and stimuli were presented on a
rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with
EXT-DVI-FM1000)]. The movie was shown at a viewing distance of \unit[63]{cm} in
\unit[720]{p} resolution at full width on a \unit[1280 $\times$ 1024]{pixel}
screen with \unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5
$\times$ 21.2]{cm}, corresponding to \unit[23.75 $\times$ 13.5] or \unit[23.75
$times$ 10.25]{cm} when considering only the movie content and excluding the
horizontal gray bars.

In both studies [+++???+++] auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by at least \unit[20–30]{dB}.
Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.

@@

% AO (Hanke, 2014)
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices & FOV
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a 10 percent inter-slice gap were recorded in ascending order.
Slices were oriented to include the ventral portions of frontal and order.
Slices were oriented to include the ventral the ventral portions of frontal and
occipital cortex while minimizing intersection with the eyeballs.  The field of
view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [Oh, S. et
al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]. Auxiliary scans
for slice alignment and motion- and distortion-correction were performed at the
beginning of the first fMRI recording session and also after the break at the
start of the recording for the second half of the movie.

% AV (Hanke, 2016)
In the AV study, a whole-body \unit[3]{Tesla} Philips Achieva dStream MRI
scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar
images (gradient-echo, \unit[2]{s} repetition time (TR), \unit[30]{ms} echo
time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth, parallel
acquisition with sensitivity encoding (SENSE) reduction factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order. Philips' ``SmartExam'' was
used to automatically position slices in AC-PC orientation such that the topmost
slice was located at the superior edge of the brain.
\todo[inline]{In the LOC study\dots}

@@

\todo[inline]{downsampling der 7T Daten}

% data source
fMRI time series data were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data are already aligned to a subject-specific
\href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3
Tesla BOLD template} by a rigid body transformation in MCFLIRT
\citep{jenkinson2002registration} to correct for motion during scanning
\citep{sengupta2016extension}.

@@

>>>>

\todo[inline]{Nach wie vor recht ausführlich; Reihenfolge der subsections mag
``inkorrekt'' sein.}

% Intro
We used data from three publicly available datsets as part of the studyforrest
dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already
been used by other research groups for independent research questions before.
% used studies
We fMRI data from three different studies. The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding, nguyen2016integration}.
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}, a dataset already used by
\citep{ben2018hippocampal}.
% VIS
c) participating in a dedicated six-category
block-design visual localizer (VIS study) \citep{sengupta2016extension}, a dataset aready used by \citep{jiahui2019predicting}.

@@

@@

\todo[inline]{inner join von AO \& AV: N=14; AO: N=19; es fehlt in beiden VP10;
Angaben zu Alter (Durchschnitt; ggf. Range) und Geschlecht sind folglich falsch
=> hier stehen lassen und unter Data erwähnen, dass die nicht benutzt wurde}
% AO study
In the AO study, 19 German native speakers (all right-handed, age 21–38 years,
mean age 26.6 years, 12 male) listened to the German audio-description
\citep{ForrestGumpGermanAD} of the movie ``Forrest Gump''
\citep{ForrestGumpMovie} as an additional audio track for visually impaired
listeners on Swiss public television.  was Germin
% AV study
In the AV study, 15 participants (21–39 years, mean age 29.4, six female) of the
prior AO study watched the audio-visual movie with dubbed German audio track
\citep{ForrestGumpDVD}.
% VIS study
In the VIS study, the same 15 participants took part in a six-category
block-design visual localizer.
% participants' health
All participants reported to have normal hearing, normal or corrected-to-normal
vision, and no known history of neurological disorders.
% compensation, consent and shit
In all both studies, participants received monetary compensation and gave
written informed consent for their participation and for public sharing of all
obtained data in anonymized form. The studies had prior approval by the Ethics
Committee of Otto-von-Guericke University of Magdeburg, Germany.

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of
the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
temporally aligned audio-description (i.e. the audio-only variant of the movie)
that was broadcast as an additional audio track for visually impaired listeners
on Swiss public television \citep{ForrestGumpGermanAD}.
% AO vs. AV: differences
The plot of the movie is already carried by an off-screen voice of the main
character Forrest Gump.  In the largely identical audio-description, a male
narrator additionally describes essential aspects of the visual scenery when
there is no off-screen voice, dialog, or other relevant auditory content.

% AO & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$2h
\citep{hanke2014audiomovie, hanke2016simultaneous}. Both stimuli were further
processed (filtering, volume adjustments) to improve audibility during MRI
scanning. Finally, each stimulus was split into eight segments of approximately
15 minutes. Except for the first movie segment, each segment started with a
snippet of at least six seconds immediately preceding the movie scene boundary
used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}.
% AV: grey bars
Black horizontal bars at the top and bottom of stimulus of the AV study were
replaced with medium-gray bars of the same size in order to increase back-
ground illumination for a more pleasant experience.

% VIS study
% picture categories
All stimuli for the VIS study were used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (matched in
luminance, size of 400 $\times$\unit[400]{px}) from each of six stimulus
categories: human faces, human bodies without heads, small objects, houses and
outdoor scenes comprising of nature and street scenes, and phase scrambled
images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.

@@

\subsection{Procedure}
% questionnaire
In all three studies, participants filled out a questionnaire on their basic
demographic information (and familiarity with the audio-description or movie).
% AO & AV: instructions
Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions respectively.  Between sessions, participants
left the scanner for a break with a flexible duration. Structural images were
obtained during the first study on a day different from the fMRI session.
% VIS: presentation & instructions
In the VIS study, participants were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run, while they also performed a one-back matching task to keep them attentive.

@@

% paradigm implementation
In all three studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.

% AO
In the AO study, visual instructions were presented on a rear-projection screen
inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue. [The screen contained a solid black ``fixation'' dot that faded in and
out at the beginning and end of a movie segment.]

% AV & VIS
In the AV and VIS study, visual instructions and stimuli were presented on a
rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with
EXT-DVI-FM1000)].
% screen size
The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p}
resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with
\unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$
21.2]{cm}.
% angle of view: AV
In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
$times$ 10.25]{cm} when considering only the movie content and excluding the
horizontal gray bars.
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.

\todo[inline]{Ist richtig, dass auditory stimulation in beiden Experimenten die
gleiche war?}

% AO & AV: auditory stimulation
In the AO and AV study, auditory stimulation was delivered through an MR confon
mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg,
Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by
at least \unit[20–30]{dB}. Headphones were fed from an Aureon 7.1 USB
(Terratec) sound card through an optical connection.

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices & FOV
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a 10 percent inter-slice gap were recorded in ascending order.
Slices were oriented to include the ventral portions of frontal and order.
Slices were oriented to include the ventral the ventral portions of frontal and
occipital cortex while minimizing intersection with the eyeballs.  The field of
view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [Oh, S. et
al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]. Auxiliary scans
for slice alignment and motion- and distortion-correction were performed at the
beginning of the first fMRI recording session and also after the break at the
start of the recording for the second half of the movie.

% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time (TR),
\unit[30]{ms} echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px}
bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction
factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order. Philips' ``SmartExam'' was
used to automatically position slices in AC-PC orientation such that the topmost
slice was located at the superior edge of the brain. This automatic slice
positioning procedure was identical in the AV und VIS study and yielded a
congruent geometry across paradigms.

@@

\todo[inline]{Satz zum Downsampling der 7T Daten? => check github repo}

\todo[inline]{subject 10 was dropped due to excessive motion: see Hanke 2016}
% data source
fMRI time series data were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data are already aligned to a subject-specific
\href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3
Tesla BOLD template} by a rigid body transformation in MCFLIRT
\citep{jenkinson2002registration} to correct for motion during scanning
\citep{sengupta2016extension}.

@@

\todo[inline]{Nouns, die eigentlich zu einer anderen Kateogrie als setting\_new
    or setting\_old gehören, aber einen Settingwechsel anzeigen, werden als
Event eines der Settingwechsel zugehörig gezählt.}
